On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 arity1.tex
Update arity1.tex
Pyramid with numbers again
I don't know why the previous changes do not show up. I tried this like
3 times already and to me it showed that it worked. In any case, here
goes the numbered pyramid again.
Small change

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./Fig/chichenBig}
	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. Beads: '$0$' black, '$1$' red, '$2$' red with black contour, '$3$' green, '$4$' green with black contour.}
	\label{CI:big}
\end{figure}

@@

\begin{enumerate}
	\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$. Now consider bead $i+2$. For $i+1$ to be fixed at $(2,1)$, $i+2$ needs to form a bond somewhere, otherwise $i+2$ could go to $(2,1)$ forming the bond with the bead at $(2,0)$ and there would be two conformations with the maximal $1$ bond. The only possibility is that there is a bead at $(3,0)$ and $i+2$ can bond with it when placed at $(3,1)$. We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by active beads, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$. Such an $m$ exists, and it is not greater than $n$. Then, bead $i+\ell$ is fixed at $(\ell+1,1)$ and bonds with $(\ell+1,0)$. However, bead $i+2+m$ cannot be fixed anywhere, because $i+2+m$ and $i+3+m$ can only add one bond to the conformation, and that is possible either with $i+2+m \rightarrow (2+m,1)$, $i+3+m \rightarrow (3+m,1)$ or with $i+2+m \rightarrow (2+m,2)$, $i+3+m \rightarrow (2+m,1)$. 
	\begin{figure}
		\centering
		\includegraphics[width=0.9\linewidth]{./Fig/hexagonOut2}
		\caption{}
		\label{fig:hexagonout2}
	\end{figure}

@@

	\caption{}
	\label{fig:hexagonOut2}
\end{figure}

@@

    \end{tabular}
    \caption{Two conformations when a bead $i-1$ at (0,0) has a free hand}
    \label{fig:beadi}
  \end{center}
\end{figure}

@@

It can yield finite conformation and the length is $3n^2+n^2+1$.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./Fig/CI_Numbers}
	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. }
	\label{CI:big}
\end{figure}

@@

\begin{enumerate}
	\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$. Now consider bead $i+2$. For $i+1$ to be fixed at $(2,1)$, $i+2$ needs to form a bond somewhere, otherwise $i+2$ could go to $(2,1)$ forming the bond with the bead at $(2,0)$ and there would be two conformations with the maximal $1$ bond. The only possibility is that there is a bead at $(3,0)$ and $i+2$ can bond with it when placed at $(3,1)$. We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by active beads, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$. Such an $m$ exists, and it is not greater than $n$. Then, bead $i+\ell$ is fixed at $(\ell+1,1)$ and bonds with $(\ell+1,0)$. However, bead $i+2+m$ cannot be fixed anywhere, because $i+2+m$ and $i+3+m$ can only add one bond to the conformation, and that is possible either with $i+2+m \rightarrow (2+m,1)$, $i+3+m \rightarrow (3+m,1)$ or with $i+2+m \rightarrow (2+m,2)$, $i+3+m \rightarrow (2+m,1)$. 
	\begin{figure}
		\centering
		\includegraphics[width=0.9\linewidth]{./Fig/hexagonOut2}
		\caption{When bead $i+2+m$ is fixed}
		\label{fig:hexagonout2}
	\end{figure}

@@

	\caption{When bead $i+1$ is fixed at (0,1)}
	\label{fig:hexagonOut2}
\end{figure}

@@

    \end{tabular}
    \caption{Two conformations when bead $i-1$ at (0,0) has a free hand}
    \label{fig:beadi}
  \end{center}
\end{figure}

@@

It can yield only finite conformation and the length is $3n^2+n^2+1$.
